Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-16 write-ups/PLDI/paper.tex
Space

\mytablong\ref{tab:applications} gives an overview of the 8 irregular
algorithms that we ported to cooperative kernels. Among them, 6 are
graph algorithms, based on Pannotia~\cite{Pannotia} and
Lonestar~\cite{BNP12} GPU application suites, using global barriers.  We
indicate how many of the original number of barriers are changed to
resizing barriers, and how many variables need to be transmitted.  In
all cases all barriers were converted, except for bc which contains
barriers deeper in the call stack, a case not supported by our
prototype. Still, these barriers could in principle also be
converted. The remaining 2 algorithms are workstealing applications:
each required the addition of $\offerfork$ and $\offerkill$ at the start
of the main loop, and no variables needed to be transmitted.  For all
these examples the porting to cooperative kernels was similarly
straightforward to the porting illustrated in
\mysec\ref{sec:programmingguidelines} for our running examples, and did
not require reshaping of the original algorithm. Most graph come with 2
different data sets as input, leading to 13 application/input pairs in
total.

>>>>

\mytablong\ref{tab:applications} gives an overview of the 8 irregular
algorithms that we ported to cooperative kernels. Among them, 6 are
graph algorithms, based on the Pannotia~\cite{Pannotia} and
Lonestar~\cite{BNP12} GPU application suites, using global barriers.  We
indicate how many of the original number of barriers are changed to
resizing barriers, and how many variables need to be transmitted.  In
all cases all barriers were converted, except for bc which contains
barriers deeper in the call stack, a case not supported by our
prototype although these barriers could in principle be
converted. The remaining 2 algorithms are workstealing applications:
each required the addition of $\offerfork$ and $\offerkill$ at the start
of the main loop, and no variables needed to be transmitted.  For all
these examples the porting to cooperative kernels was similarly
straightforward to the porting illustrated in
\mysec\ref{sec:programmingguidelines} for our running examples. Most graph come with 2
different data sets as input, leading to 13 application/input pairs in
total.
